ggalluvial: Layered Grammar for Alluvial Plots

### 2022-08-21 README.rmd
link to edav community contribution project page
credit specific students and links

>>>>

### Short form

For some more digestible guidance on using **ggalluvial**, check out three cheat sheets and demos by students in Joyce Robbins's [Exploratory Data Analysis and Visualization Community Contribution Project](https://jtr13.github.io/cc21fall2/index.html):

* an [introduction](https://jtr13.github.io/cc21fall2/ggalluvial-cheatsheet.html) by Meggie Wen (Chapter 33)
* a [cheat sheet](https://cheatography.com/seleven/cheat-sheets/ggalluvial/) by Qingyi Zhang (Chapter 14)
* a [blog about how this package implements alluvial plots](https://medium.com/@arnavsaxena96/all-about-alluvial-diagrams-21da1505520b) by Arnav Saxena (Chapter 134)
